Cui2020Rep_SumWeightsBarPlots

### 2022-08-30 Cui2020Rep_SumWeightsBarPlots.Rmd
plots figure S2

>>>>

# PC1 - Replication Sample
```{r}
# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC1_testB.mat'));
Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix

Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
        axis.text.y = element_text(size= 31, color = "black"),
        axis.title=element_text(size = 31)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
                              13, 14, 15, 16, 17),
                   labels = as.character(Rank))
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC1_testB_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
```

# PC2 - Replication Sample
```{r}
# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC2_testB.mat'));
Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix

Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
        axis.text.y = element_text(size= 31, color = "black"),
        axis.title=element_text(size = 31)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
                              13, 14, 15, 16, 17),
                   labels = as.character(Rank))
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC2_testB_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
```

# PC3 - Replication Sample
```{r}
# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC3_testB.mat'));
Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix

Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
        axis.text.y = element_text(size= 31, color = "black"),
        axis.title=element_text(size = 31)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
                              13, 14, 15, 16, 17),
                   labels = as.character(Rank))
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC3_testB_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
```
